### 2021-02-18 README.Rmd
Done "Identify all focal and corresponding competitor trees" section
update README

1. Compute growth of trees based on census data
1. Add spatial information
1. Compute focal versus competitor tree information
1. Fit model and make predictions
1. Run spatial cross-validation

@@

```{r}
focal_vs_comp_ex <- focal_vs_comp_ex %>%
  mutate(growth_hat = predict(comp_bayes_lm_ex, focal_vs_comp_ex))
focal_vs_comp_ex
```

>>>>

1. Compute growth of trees based on census data
1. Add spatial information
1. Identify all focal and corresponding competitor trees
1. Fit model and make predictions
1. Run spatial cross-validation

@@

```{r}
focal_vs_comp_ex <- focal_vs_comp_ex %>%
  mutate(growth_hat = predict(comp_bayes_lm_ex, newdata = focal_vs_comp_ex))
focal_vs_comp_ex
```
